---
title: "Chapter 18 Missing values learning notes"
author: "Hao Wang"
date: "2023-12-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# library
```{r}
library(tidyverse)
library(nycflights13)
```

# 18.2

```{r}
treatment <- tribble(
  ~person,           ~treatment, ~response,
  "Derrick Whitmore", 1,         7,
  NA,                 2,         10,
  NA,                 3,         NA,
  "Katherine Burke",  1,         4
)

treatment
```

Use “last observation carried forward” to fill the NA.

```{r}
treatment |> 
  fill(everything())
```

# 18.3 implicit missing values

```{r}
stocks <- tibble(
  year  = c(2020, 2020, 2020, 2020, 2021, 2021, 2021),
  qtr   = c(   1,    2,    3,    4,    2,    3,    4),
  price = c(1.88, 0.59, 0.35,   NA, 0.92, 0.17, 2.66)
)
stocks
```

```{r}
stocks |>
  pivot_wider(
    names_from = qtr, 
    values_from = price
  )
#> # A tibble: 2 × 5
#>    year   `1`   `2`   `3`   `4`
#>   <dbl> <dbl> <dbl> <dbl> <dbl>
#> 1  2020  1.88  0.59  0.35 NA   
#> 2  2021 NA     0.92  0.17  2.66
```
Use the function complete().

tidyr::complete() allows you to generate explicit missing values by providing a set of variables that define the combination of rows that should exist.

```{r}
stocks |> 
  complete(year, qtr)
```
 Provide more years to the data.
 
```{r}
stocks |> 
  complete(year = 2019:2021, qtr)
```

Use anti_join(). airports and planes are two tables in nycflights13.

```{r}
flights |> 
  distinct(faa = dest) |> 
  anti_join(airports)
#> Joining with `by = join_by(faa)`
#> # A tibble: 4 × 1
#>   faa  
#>   <chr>
#> 1 BQN  
#> 2 SJU  
#> 3 STT  
#> 4 PSE

flights |> 
  distinct(tailnum) |> 
  anti_join(planes)
#> Joining with `by = join_by(tailnum)`
#> # A tibble: 722 × 1
#>   tailnum
#>   <chr>  
#> 1 N3ALAA 
#> 2 N3DUAA 
#> 3 N542MQ 
#> 4 N730MQ 
#> 5 N9EAMQ 
#> 6 N532UA 
#> # ℹ 716 more rows
```

# 18.4

```{r}
health <- tibble(
  name   = c("Ikaia", "Oletta", "Leriah", "Dashay", "Tresaun"),
  smoker = factor(c("no", "no", "no", "no", "no"), levels = c("yes", "no")),
  age    = c(34, 88, 75, 47, 56),
)

health
```
```{r}
health |> count(smoker)
```
Keep all levels in the factor.

```{r}
health |> count(smoker, .drop = F)
```
In ggplot()
```{r}
health |> 
  ggplot(aes(x = smoker)) +
  geom_bar() +
  scale_x_discrete()

health |> 
  ggplot(aes(x = smoker)) +
  geom_bar() +
  scale_x_discrete(drop = F)
```



















