---
title: "Chapter 4 learning notes"
author: "Hao Wang"
date: "2023-12-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(nycflights13)
```

# 4.1

This is to learn the coding style.

Variables names should only include lowercase letters, numbers and \_.

-   **long name** As a general rule of thumb, it’s better to prefer long, descriptive names that are easy to understand rather than concise names that are fast to type.

-   **Rename**: If you have a bunch of names for related things, do your best to be consistent. It’s easy for inconsistencies to arise when you forget a previous convention, so don’t feel bad if you have to go back and rename things. In general, if you have a bunch of variables that are a variation on a theme, you’re better off giving them a common prefix rather than a common suffix because autocomplete works best on the start of a variable.

-   **file name**:

-- File names should be machine readable: avoid spaces, symbols, and special characters. Don’t rely on case sensitivity to distinguish files. Use '-' to replace space. -- File names should be human readable: use file names to describe what’s in the file. -- File names should play well with default ordering: start file names with numbers so that alphabetical sorting puts them in the order they get used. For example:

```
01-load-data.R
02-exploratory-analysis.R
03-model-approach-1.R
04-model-approach-2.R
fig-01.png
fig-02.png
report-2022-03-20.qmd
report-2022-04-02.qmd
report-draft-notes.txt

```

# 4.6 Exercise

```{r}
flights |>
  filter(dest == "IAH") |>
  group_by(year, month, day) |>
  summarize(
    n = n(),
    delay = mean(arr_delay, na.rm = TRUE)
  ) |>
  filter(n > 10)

flights |>
  filter(
    carrier == "UA",
    dest %in% c("IAH", "HOU"),
    sched_dep_time > 0900,
    sched_arr_time < 2000
  ) |>
  group_by(flight) |>
  summarize(
    delay = mean(arr_delay, na.rm = TRUE),
    cancelled = sum(is.na(arr_delay)),
    n = n()
  ) |>
  filter(n > 10)
```
