---
title: "Chapter 25"
author: "Hao Wang"
date: "2023-12-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(nycflights13)
```

## Intro

study notes for chapter 25 function

## 25.2 vector fuction

```{r func rescale01}
rescale01 <- function(x) {
  
  rng <- range(x, na.rm = T, finite = T)
  (x - rng[1]) / (rng[2] - rng[1])
}

```


```{r}
x <- c(1:10, Inf)
rescale01(x)
#>  [1]   0   0   0   0   0   0   0   0   0   0 NaN
```
### 25.2.5 Exercise

Q 1.
```{r}
mean(is.na(x))
mean(is.na(y))
mean(is.na(z))

x / sum(x, na.rm = TRUE)
y / sum(y, na.rm = TRUE)
z / sum(z, na.rm = TRUE)

round(x / sum(x, na.rm = TRUE) * 100, 1)
round(y / sum(y, na.rm = TRUE) * 100, 1)
round(z / sum(z, na.rm = TRUE) * 100, 1)
```

A: calculate the percentage of missing value in a vector
```{r}
pct_missing <- function(x){
  mean(is.na(x))
}
```

```{r}
x <- c(1:99, NA)
pct_missing(x)
```
fraction of sum of a vector
```{r}
pct_sum <- function(x){
  x / sum(x, na.rm = T)
}

pct_sum(x)
```

q2: In the second variant of rescale01(), infinite values are left unchanged. 
Can you rewrite rescale01() so that -Inf is mapped to 0, and Inf is mapped to 1?

```{r}
rescale02 <- function(x) {
  x <- case_when(
    x == -Inf ~ 0,
    x == Inf ~ 1,
    .default = x
  )
  rng <- range(x, na.rm = T, finite = T)
  (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
y <- c(1:10, -Inf, Inf)
rescale02(y)
```
q 6: Read the documentation to figure out what the following functions do. Why are they useful even though they are so short?

```{r}
is_directory <- function(x) {
  file.info(x)$isdir
}
is_readable <- function(x) {
  file.access(x, 4) == 0
}
```

```{r}
file.info("chapter-4.Rmd")

file.access("chapter-4.Rmd", 4)
```
### 25.3.4 Data-masking vs. tidy-selection

Sometimes you want to select variables inside a function that uses data-masking instead of tidy-selection. For example, the group_by() in following function count_missing(). You need to use the function pick() with embrace to make the data-masking work.

```{r}
count_missing <- function(df, group_vars, x_var) {
  df |> 
    group_by(pick({{ group_vars }})) |> 
    summarize(
      n_miss = sum(is.na({{ x_var }})),
      .groups = "drop"
  )
}

```

```{r}
flights |> count_missing(c(year, month), dep_time)
```





























